---
title: "Lab 00 - Hello IDS!"
author: "Kaitlin Fong"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kaitlin", "Isabel", "Charlotte", 
           "Jamie", "Alfredo","Lucien"),
  github_username = c("KaitlinF5", "Shaojiaxi1003", "Xxinnnnn", 
                      "JamieAdamiec", "sunmenghchuan", "LucienZhang1110"), 
  colour = c("Yellow", "Blue", "Purple", 
             "Red", "White", "Purple"),
  hobby = c("Maths", "Sleeping", "Shopping", 
            "Gym", "Badminton","Reading"),
  favourite_number = c(7, 7, 7, 5, 5,5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*The plot shows each person's favourite number on a bar graph along with their favourite colours. It also identifies each person by their github username.*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Favourite Number", 
          y = "GitHub Username",
          title = "Team Datalab")
```

*labs function lables the axis of the plot*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*the plot doesn't show *
